---
title: "p8105_hw1_yj2803"
author: "Yuki Joyama"
date: "2023-09-23"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

# Problem 1
```{r data, results='hide'}
library(moderndive)
data("early_january_weather") # data set in moderndive library
```

The dataset "early_january_weather" contains the following variables:  
`r ls(early_january_weather)`  
It has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.  
The mean temperature (temp) in this dataset is `r round(mean(early_january_weather$temp), digits = 2)`°F.

## The relationship among temperature, time in hour, and humidity
```{r scatter, cache=T, message=F}
library(ggplot2)
scatter_temp_hour <- early_january_weather %>% 
  ggplot(aes(x=time_hour, y=temp, color=humid)) + # color points using the humid variable
  geom_point(size=2) 
scatter_temp_hour

ggsave("scatter_temp_hour.pdf", plot = last_plot(), path = "/Users/yukijoyama/Library/CloudStorage/GoogleDrive-jikeyu1995@gmail.com/My Drive/version_control/MS-biostats/Data Science 1/p8105_hw1_yj2803") # save the scatterplot in the working directory
```

The scatterplot shows that temperatures fluctuate within a day and tend to increase toward mid-January.
Humidity seems to tend to decrease as temperatures increase and increase as temperatures go down. However, a few days of generally high humidity were observed at the end of the second week of January.  

# Problem 2

## Creating a dataframe 
```{r tidyverse, message=F}
library(tidyverse)
```

```{r sample, echo=T}
df <- tibble(
  norm_samp = rnorm(10), # create a random sample of size 10 from a standard normal distribution
  norm_samp_log = norm_samp > 0, # a logical vector indicating if elements in df are greater then 0
  norm_samp_char = c("Potato", "Onion", "Carrot", "Beef", "Tofu", "Shiitake", "Soysauce", "Salt", "Scallion", "Bokchoy"), # a character vector of length 10
  norm_samp_factor = c("Vegetable", "Vegetable", "Vegetable", "Protein", "Protein", "Vegetable", "Seasoning", "Seasoning", "Vegetable", "Vegetable") %>%
  factor() # a factor vector of length 10, with 3 different factor levels
)
df
```

## Mean of each variable

Now, we take the mean of each variable in the above dataframe. 

```{r means, echo=T}
mean_samp <- mean(pull(df, norm_samp)) %>% 
  print() # mean of a norm_samp in df

mean_log <- mean(pull(df, norm_samp_log)) %>% 
  print() # mean of a norm_samp_log in df

mean_char <- mean(pull(df, norm_samp_char)) %>% 
  print() # mean of a norm_samp_char in df

mean_factor <- mean(pull(df, norm_samp_factor)) %>% 
  print() # mean of a norm_samp_factor in df
```

As shown in the outputs, norm_samp and norm_samp_log returned valid means, while norm_samp_char and norm_samp_factor returned errors.  

## Converting variables into numeric

```{r conversion, echo=T, results='hide', warning=F}
as.numeric(df$norm_samp_log) # logical -> numeric
as.numeric(df$norm_samp_char) # character -> numeric
as.numeric(df$norm_samp_factor) # factor -> numeric
```

When the as.numeric function was applied to the dataframe, the logical and factor vectors were successfully replaced by numeric values. No change was observed in the character vector.
This is because the as.numeric function converts TRUE to 1 and FALSE to 0 for the logical vector, and returns the numeric code corresponding to the factor level for the factor vector. Numeric values cannot be assigned to a character vector unless it consists of a numeric value in character form (e.g., "1", "2", etc.). 

Since there are two variables in the logical vector that can be converted to binary numbers, the mean function can return values in the proportion of TRUE (1). The mean function could not be applied for the character and factor vector in the dataframe because they are not numeric or logical. Only after successfully converting them to numeric values can the mean function be expected to return a valid value.


