---
title: "p8105_hw1_yj2803"
author: "Yuki Joyama"
date: "2023-09-23"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

# Problem 1
```{r data, results='hide'}
library(moderndive)
data("early_january_weather") # data set in moderndive library
```

The dataset "early_january_weather" contains the following variables:  
`r ls(early_january_weather)`  
It has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.  
The mean temperature (temp) in this dataset is `r round(mean(early_january_weather$temp), digits = 2)`°F.

## The relationship among temperature, time in hour, and humidity
```{r scatter, cache=T, message=F}
library(ggplot2)
scatter_temp_hour <- early_january_weather %>% 
  ggplot(aes(x=time_hour, y=temp, color=humid)) + # color points using the humid variable
  geom_point(size=2) 
scatter_temp_hour

ggsave("scatter_temp_hour.pdf", plot = last_plot(), path = "/Users/yukijoyama/Library/CloudStorage/GoogleDrive-jikeyu1995@gmail.com/My Drive/version_control/MS-biostats/Data Science 1/p8105_hw1_yj2803") # save the scatterplot in the working directory
```

The scatterplot shows that temperatures fluctuate within a day and tend to increase toward mid-January.
Humidity seems to tend to decrease as temperatures increase and increase as temperatures go down. However, a few days of generally high humidity were observed at the end of the second week of January.  




